### 2024-05-06 project3/draft.tex
new

In the context of hedging VAs, the state space is partially observed.
The agent does not have access to the contract specifications and the underlying risk factors.
Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
To address the non-Markovian dynamics, an LSTM component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
This approach is known as recurrent PPO~\citep{ni2021recurrent}.
Let $h_t$ be the hidden state of the LSTM at time $t$.
The state representation $\mathbf{s}_t$ with recurrent PPO is defined as:
\begin{equation}
    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}, h_t)
\end{equation}
Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.

>>>>

In the context of hedging VAs, the state space is partially observed.
The agent does not have access to the contract specifications and the underlying risk factors.
Furthermore, a rough volatility model introduces non-Markovian dynamics, i.e., the future state of the system depends on the entire history of the system.
To address the non-Markovian dynamics, an LSTM component is added to the state representation $\mathbf{s}_t$ to capture the temporal dependencies in the data.
This approach is known as recurrent PPO~\citep{ni2021recurrent}.
Let $h_t$ be the hidden state of the LSTM at time $t$.
The state representation $\mathbf{s}_t$ with recurrent PPO is defined as:
\begin{equation} \label{eq3:stateRNN}
    \mathbf{s}_t = (S_t, F_t, G_t, \tau, \Delta_{t-1}, h_t)
\end{equation}
The policy and reward function remain the same but with the new state representation in Equation~\ref{eq3:stateRNN}.
Instead of following the standard PPO algorithm, the agent uses the recurrent PPO algorithm to learn an optimal policy for hedging VAs.
